DATA 621 - Business Analytics and Data Mining

### 2020-11-10 HW4/HW4_Draft.Rmd
tidyverse loads so many packages and masks so many calls, that I put it first to allow the other packages a chance.

```{r loadData, include=FALSE}
# Load necessary libraries
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(pROC)
library(mice)
library(arm)
library(corrplot)
library(data.table)
library(tidyverse)

>>>>

```{r loadData, include=FALSE}
# Load necessary libraries
library(tidyverse)
library(ggplot2)
library(scales)
library(knitr)
library(caret)
library(RANN)
library(pROC)
library(mice)
library(arm)
library(corrplot)
library(data.table)
